Urbanization affects web abundance and aggregation of a funnel-weaving spider, *Agelenopsis pennsylvanica*

### 2023-01-08 manuscript/figures_tables.Rmd
Some more manuscript edits
Lots of changes

>>>>

```{r references, fig.width = 3.77, dpi = 300, out.width="50%", include = FALSE}
#Examples of studies elucidating the mechanisms behind spider aggregations. Mechanisms are categorized by inter- and intraspecific interactions, environmental factors, and dispersal, but it is important to note that these categories are likely inter-related. The table is meant to provide examples, rather than represent a full review of studies. Several aggregation mechanisms were studied in urban habitats.

knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/references.png")
```
